|

### 2021-09-09 appendix/appendix.Rmd
descrip stats moderators, reg coeff dv

# Estimation of the 
estim_het <- function(dat, yi, v, random, slab, hetvar = NULL) {
  if (is.null(hetvar)) {
    stop('Hetvar should be different than null.')
  }
  levshetvar <- unique(hetvar)
  fullmod <- rma.mv(yi = yi, V = v, random = random,
                    data = dat, slab = slab, method = 'REML',
                    test = 't', tdist = T)
  res <- tibble()
  for (i in levshetvar) {
    partmod <- rma.mv(yi = yi, V = v, 
                      random = random,
                      data = dat, slab = slab, 
                      method = 'REML',
                      test = 't', tdist = T, 
                      subset = hetvar == i)
    partmod <- broom_mod(partmod, subgroup = T)
    partmod$byvar = i
    partmod <- bind_rows(
      tibble(TE = NA, seTE = NA,
             studlab = toupper(i), lower = NA,
             upper = NA, group = "B", byvar = i),
      partmod
    )
    res <- bind_rows(res, partmod)
  }
  aux <- data.frame(predict(fullmod))
  res <- bind_rows(res,
                   tibble(
                     byvar = NA,
                     TE = c(aux$pred, NA),
                     seTE = c(aux$se, NA),
                     studlab = c("Overall Effect", "Prediction Interval"),
                     lower = c(aux$ci.lb, aux$cr.lb),
                     upper = c(aux$ci.ub, aux$cr.ub),
                     group = "B"))
  res <- data.frame(res)
  res$byvar <- toupper(res$byvar)
  return(res)
}

@@

@@

In this section, we present the intuition behind the "law of $1/n$", as well as
the alternative "reverse law of $1/n$" proposed by @primo2008distributive.

@@

```{r, warning=F, message=F, echo = FALSE, cache=TRUE, results='asis'}
fulldat$usemeta2 <- factor(fulldat$usemeta)
levels(fulldat$usemeta2) <- c("Extended Sample", "Main Sample")
aux <- select(fulldat, usemeta2, indepvar2, year, published, method,
              instdesign, elecsys2) %>%
  mutate(indepvar2 = recode(indepvar2,
                            `N` = "Lower Chamber Size",
                            `K` = "Upper Chamber Size",
                            `logN` = "Log of Lower Chamber Size"),
         elecsys2 = recode(elecsys2,
                           `Non-Maj` = "Non-Majoritarian",
                           `Maj` = "Majoritarian")) %>%
  rename(`Independent Variables` = indepvar2,
         `Year`                  = year,
         `Published work`        = published,
         `Estimation method`     = method,
         `Institutional Design`  = instdesign,
         `Electoral system`      = elecsys2)
export2md(descrTable(~.-usemeta2, aux, y = aux$usemeta2,
                        show.p.overall = F, show.all = T),
          caption = "Descriptive Statistics of Moderators",
          format  = "latex")
```

@@

# Meta-Analysis

@@

# Meta-Analysis (All Coefficients)

@@

# Meta-Regressions (All Coefficients)

@@

>>>>

# Estimation of the heterogeneous effects
estim_het <- function(dat, yi, v, random, slab, hetvar = NULL) {
  if (is.null(hetvar)) {
    stop('Hetvar should be different than null.')
  }
  levshetvar <- unique(hetvar)
  fullmod <- rma.mv(yi = yi, V = v, random = random,
                    data = dat, slab = slab, method = 'REML',
                    test = 't', tdist = T)
  res <- tibble()
  for (i in levshetvar) {
    partmod <- rma.mv(yi = yi, V = v,
                      random = random,
                      data = dat, slab = slab,
                      method = 'REML',
                      test = 't', tdist = T,
                      subset = hetvar == i)
    partmod <- broom_mod(partmod, subgroup = T)
    partmod$byvar = i
    partmod <- bind_rows(
      tibble(TE = NA, seTE = NA,
             studlab = toupper(i), lower = NA,
             upper = NA, group = "B", byvar = i),
      partmod
    )
    res <- bind_rows(res, partmod)
  }
  aux <- data.frame(predict(fullmod))
  res <- bind_rows(res,
                   tibble(
                     byvar = NA,
                     TE = c(aux$pred, NA),
                     seTE = c(aux$se, NA),
                     studlab = c("Overall Effect", "Prediction Interval"),
                     lower = c(aux$ci.lb, aux$cr.lb),
                     upper = c(aux$ci.ub, aux$cr.ub),
                     group = "B"))
  res <- data.frame(res)
  res$byvar <- toupper(res$byvar)
  return(res)
}

@@

export2md2<-function(x, which.table="descr", nmax=TRUE, header.labels=c(),
                    caption=NULL, format="html", width=Inf,
                    strip=FALSE, first.strip=FALSE, background="#D2D2D2",
                    size=NULL, landscape=FALSE,
                    header.background=NULL, header.color=NULL,
                    position="center", ...){

  trim <- function(x){
    x <- gsub("^[ ]+","",x)
    x <- gsub("[ ]+$","",x)
    x
  }

  prepare <- function (x, nmax, header.labels)
    {

        # x <- tab[1:3]
        # nmax <- TRUE
        # header.labels <- c()
        # names(attributes(x))

        show.all <- attr(x, "show.all")
        show.descr <- attr(x, "show.descr")
        groups <- attr(x, "groups")
        ny <- attr(x, "ny")
        all.last <- attr(x, "all.last")

        varnames <- attr(x, "varnames")
        nr <- attr(x, "nr")
        desc <- x$desc
        avail <- x$avail
        nmax.pos <- attr(x, "nmax.pos")
        nmax.avail.pos <- NULL
        if (length(nmax.pos[[1]]) == 0 & length(nmax.pos[[2]]) == 0) nmax.avail.pos <- integer(0)
        if (length(nmax.pos[[1]]) == 0 & length(nmax.pos[[2]]) > 0) nmax.avail.pos <- nmax.pos[[2]] + 1
        if (length(nmax.pos[[1]]) > 0 & length(nmax.pos[[2]]) == 0) nmax.avail.pos <- 1
        if (length(nmax.pos[[1]]) > 0 & length(nmax.pos[[2]]) > 0) nmax.avail.pos <- c(1, nmax.pos[[2]])
        if (length(nmax.avail.pos) > 0 && nmax) {
            Nmax <- apply(avail[, nmax.avail.pos, drop = FALSE],2, function(x) max(as.double(x)))
        } else {
            Nmax <- NULL
            nmax <- FALSE
        }

        dd.pos <- attr(x, "dd.pos")
        j <- 1
        table1 <- NULL
        if (!is.null(attr(x, "caption")))
            cc <- character(0)
        for (i in 1:length(varnames)) {
            if (nr[i] == 1) {
                t.i <- desc[j, , drop = FALSE]
            } else {
                t.i <- rbind(rep(NA, ncol(desc)), desc[j:(j + nr[i] -
                                                              1), , drop = FALSE])
                rownames(t.i)[1] <- paste(varnames[i], ":", sep = "")
                rownames(t.i)[-1] <- sub(varnames[i], "", rownames(t.i)[-1], fixed = TRUE)
                rownames(t.i)[-1] <- sub(": ", "    ", rownames(t.i)[-1])
                if (length(dd.pos) < ncol(t.i)) {
                    t.i[1, -dd.pos] <- t.i[2, -dd.pos]
                    t.i[2, -dd.pos] <- NA
                }
            }
            table1 <- rbind(table1, t.i)
            j <- j + nr[i]
            if (!is.null(attr(x, "caption"))) {
                if (attr(x, "caption")[[i]] == "")
                    cc <- c(cc, rep("", NROW(t.i)))
                else cc <- c(cc, attr(x, "caption")[[i]], rep("",
                                                              NROW(t.i) - 1))
            }
        }
        if (ncol(table1) == 0) table1 <- table1[-1, ]
        if (nmax) table1 <- rbind(colnames(table1), c(paste("N=", Nmax, sep = ""), rep("", ncol(table1) - length(Nmax))), table1) else table1 <- rbind(colnames(table1), table1)
        table1 <- ifelse(is.na(table1), "", table1)
        if (length(header.labels)==6 && is.null(names(header.labels))){
            names(header.labels)<-c("all","p.overall","p.trend","ratio","p.ratio","N")
        }
        if ("all"%in%names(header.labels)){
            ww.all<-grep("^\\[ALL\\]",trim(table1[1,]))
            if (length(ww.all)>0){
                ww.all<-ww.all[1]
                table1[1,ww.all]<-header.labels["all"]
            }
        }
        if ("p.overall"%in%names(header.labels)){
            ww.p.overall<-which(table1[1,]=="p.overall")
            if (length(ww.p.overall)>0){
                ww.p.overall<-rev(ww.p.overall)[1]
                table1[1,ww.p.overall]<-header.labels["p.overall"]
            }
        }
        if ("p.trend"%in%names(header.labels)){
            ww.p.trend<-which(table1[1,]=="p.trend")
            if (length(ww.p.trend)>0){
                ww.p.trend<-rev(ww.p.trend)[1]
                table1[1,ww.p.trend]<-header.labels["p.trend"]
            }
        }
        if ("ratio"%in%names(header.labels)){
            ww.ratio<-which(table1[1,]%in%c("OR","HR"))
            if (length(ww.ratio)>0){
                ww.ratio<-rev(ww.ratio)[1]
                table1[1,ww.ratio]<-header.labels["ratio"]
            }
        }
        if ("p.ratio"%in%names(header.labels)){
            ww.p.ratio<-which(table1[1,]=="p.ratio")
            if (length(ww.p.ratio)>0){
                ww.p.ratio<-rev(ww.p.ratio)[1]
                table1[1,ww.p.ratio]<-header.labels["p.ratio"]
            }
        }
        if ("N"%in%names(header.labels)){
            ww.N<-which(table1[1,]=="N")
            if (length(ww.N)>0){
                ww.N<-rev(ww.N)[1]
                table1[1,ww.N]<-header.labels["N"]
            }
        }
        table1 <- apply(table1, 2, format, justify = "centre")
        colnames(table1) <- rep("", ncol(table1))

        table2 <- x[[2]]
        table2 <- as.matrix(table2)
        table2 <- ifelse(is.na(table2), "", table2)
        table2 <- rbind(colnames(table2), table2)
        table2 <- apply(table2, 2, format, justify = "centre")
        colnames(table2) <- rep("", ncol(table2))

        # rearrange table 1 and table 2 by putting all column after descriptives by groups.
        if (all.last & show.all & show.descr & groups){
            table1[,1:(ny+1)] <- table1[,c(2:(ny+1),1)]
        }
        if (all.last){
            table2[,1:(ny+1)] <- table2[,c(2:(ny+1),1)]
        }

        # out
        out <- list(table1 = table1, table2 = table2)
        if (!is.null(attr(x, "caption"))) attr(out, "cc") <- cc
        attr(out, "nmax") <- nmax
        nr <- ifelse(nr>1, nr+1, nr)
        nr <- cbind(nr, rep(0:1, length(nr))[1:length(nr)])
        nr <- unlist(apply(nr, 1, function(x) rep(x[2],x[1])))
        attr(out, "nr") <- nr
        out

    }

  # compiled.format <- try(rmarkdown::all_output_formats(knitr::current_input())[1],silent=TRUE)
  #
  # if (inherits(compiled.format, "try-error") || is.null(compiled.format)){
  #   warning("you are using export2md out of Rmarkdown context...")
  # } else {
  #   if (compiled.format%in%c("html_document","ioslides_presentation","slidy_presentation")) format <- "html"
  #   if (compiled.format%in%c("pdf_document","beamer_presentation")) format <- "latex"
  #   if (compiled.format=="word_document") format <- "markdown"
  # }

  if (missing(format)){
    format <- NA
    if (!interactive()){ # execute inside Rmarkdown
      if (knitr::is_html_output()) format="html"
      if (knitr::is_latex_output()) format="latex"
      if (!knitr::is_html_output() & !knitr::is_latex_output()) format="markdown"
      if (is.na(format)){
        warning("Unable to identify format -> HTML assigned.")
        format <- "html"
      }
    } else {# execute inside Rmarkdown
      warning("You are calling export2md outside Rmarkdown without specifying format -> html format is assigned")
      format <- "html"
    }
  }

  extras <- list(...)
  if (!inherits(x, "createTable"))
    stop("x must be of class 'createTable'")
  if (inherits(x, "cbind.createTable"))
    stop("x cannot be of class 'cbind.createTable'")
  ww <- charmatch(which.table, c("descr", "avail"))
  if (is.na(ww))
    stop(" argument 'which.table' must be either 'descr' or 'avail'")

  if (attr(x,"groups")){
    y.name.label<-attr(x,"yname")
  }

  if (!is.null(caption)){
    if (!is.character(caption))
      stop(" argument 'caption' must be a character'")
  } else {
    if (ww==1){
      if (attr(x,"groups"))
        if (inherits(x,"missingTable"))
          caption<-paste("Missingness table by groups of `",y.name.label,"'",sep="")
      else
        caption<-paste("Summary descriptives table by groups of `",y.name.label,"'",sep="")
      else
        if (inherits(x,"missingTable"))
          caption<-"Missingess table"
        else
          caption<-"Summary descriptives table"
    }
    if (ww==2){
      if (attr(x,"groups"))
        caption<-paste("Available data by groups of `",y.name.label,"'",sep="")
      else
        caption<-"Available data"
    }
  }
  pp <- compareGroups:::prepare(x, nmax = nmax, header.labels)
  #pp <- prepare(x, nmax = nmax, header.labels)
  cc <- unlist(attr(pp, "cc"))
  if (ww %in% c(1)) {
    table1 <- pp[[1]]
    ii <- ifelse(rownames(table1)[2] == "", 2, 1)
    table1 <- cbind(rownames(table1), table1)
    align <- c("l", rep("c", ncol(table1)))
    table1[1, 1] <- " "
    colnames(table1) <- table1[1, ]
    colnames(table1)[-1] <- trim(colnames(table1)[-1])
    table1 <- table1[-1, , drop = FALSE]
    table1[,2:ncol(table1)] <- apply(table1[,-1,drop=FALSE],2,trim)
    #table1 <- table1[-2]
    #names(table1)[1] <- 'Extended Sample'
    # N in the second row
    table1 <- table1[,-3]
    colnames(table1)[2] <- 'Extended Sample'
    n.exists <- nrow(table1) > 1 && length(grep("^N=", trim(table1[1, 2])))
    if (format=="latex" & strip)
      table1[((1+n.exists):nrow(table1)),ncol(table1)] <- ifelse(table1[((1+n.exists):nrow(table1)),ncol(table1)]=="", "\\vphantom{}", table1[((1+n.exists):nrow(table1)),ncol(table1)])
    if (format=="latex") caption <- gsub("%","\\\\%",caption)
    ans <- knitr::kable(table1, align = align, row.names = FALSE, caption=caption[1], format=format,
                        booktabs=format=="latex", longtable=TRUE, linesep="", ...)
    ans <- add_indent(ans, grep("^ ",table1[,1]))
    if (width!=Inf) ans <- column_spec(ans, 1, width = width)
    # groups
    if (!is.null(cc)){
      for (cci in 1:length(cc)){
        if (cc[cci]!=""){
          group.label <- cc[cci]
          inici <- 0
          final <- 0
        } else {
          if (cc[cci-1]!="")
            group.begin <- cci-1
          if (cci==length(cc) || cc[cci+1]!=""){
            group.end <- cci
            ans <- group_rows(ans, group.label, group.begin+n.exists, group.end+n.exists)
          }
        }
      }
    }
    if (strip){
      nr <- attr(pp, "nr")
      ans <- row_spec(ans, which(nr==!first.strip)+n.exists, background = background)
    }
    if (n.exists){
      ans <- row_spec(ans, 1, hline_after=TRUE)
    }

    if (landscape) ans <- landscape(ans)
    if (format=="latex"){
      ans <- kable_styling(ans, latex_options = c("repeat_header"), font_size=size, position=position)
      #if (n.exists) ans <- gsub("\\\\midrule", "", ans) # remove lines after N
      if (n.exists) ans <- gsub("\\\\midrule\n\\\\endfirsthead", "\\\\endfirsthead", ans) # remove lines after N
      if (strip) ans <- gsub("\\textbackslash{}vphantom\\{\\}", "\\vphantom{}", ans, fixed=TRUE)
    }
    if (format=="html"){
      ans <- kable_styling(ans, bootstrap_options=c(if (!strip) "striped" else NULL, "condensed"), full_width=FALSE, font_size=size, position=position)
      ans <- row_spec(ans, 0, background=header.background, color=header.color)
      ans <- row_spec(ans, if (sum(unlist(attr(x, "nmax.pos")))>0) 1 else 0, italic=sum(unlist(attr(x, "nmax.pos")))>0, extra_css = "border-bottom: 1px solid grey")
    }
    return(ans)
  }
  if (ww %in% c(2)){
    # table2 <- compareGroups:::prepare(x, nmax = nmax, c())[[2]]
    table2 <- prepare(x, nmax = nmax, c())[[2]]
    table2 <- cbind(rownames(table2), table2)
    if (!is.null(attr(x, "caption"))) {
      cc <- unlist(attr(x, "caption"))
      table2[, 1] <- paste("    ", table2[, 1])
    }
    table2[1, 1] <- " "
    align <- c("l", rep("c", ncol(table2)))
    colnames(table2)[-1] <- trim(table2[1, -1])
    table2 <- table2[-1, ,drop=FALSE]
    ans <- knitr::kable(table2, align = align, row.names = FALSE, caption=caption[1], format=format, booktabs=format=="latex", longtable=TRUE, ...)
    # ans <- knitr::kable(table2, align = align, row.names = FALSE, caption=caption[1], format=format, booktabs=format=="latex")
    # groups
    if (!is.null(cc)){
      for (cci in 1:length(cc)){
        if (cc[cci]!=""){
          group.label <- cc[cci]
          inici <- 0
          final <- 0
        } else {
          if (cc[cci-1]!="")
            group.begin <- cci-1
          if (cci==length(cc) || cc[cci+1]!=""){
            group.end <- cci
            ans <- group_rows(ans, group.label, group.begin, group.end)
          }
        }
      }
    }
    ans <- add_indent(ans, integer())
    if (strip) ans <- row_spec(ans, which(rep(0:1, nrow(table2))[1:nrow(table2)]==!first.strip), background = background)
    if (width!=Inf) ans <- column_spec(ans, 1, width = width)
    if (landscape) ans <- landscape(ans)
    if (format=="latex"){
      ans <- kable_styling(ans, latex_options = c("repeat_header"), font_size = size, position=position)
    }
    if (format=="html"){
      ans <- kable_styling(ans, bootstrap_options=c(if (!strip) "striped" else NULL, "condensed"), full_width = FALSE, font_size = size, position=position)
      ans <- row_spec(ans, 0, background=header.background, color=header.color)
      ans <- row_spec(ans, 0, italic=FALSE, extra_css = "border-bottom: 1px solid grey")
    }

    return(ans)
  }
}

@@

Here we present the intuition behind the "law of $1/n$", as well as the
alternative "reverse law of $1/n$" proposed by @primo2008distributive.

@@

```{r, warning=F, message=F, echo = FALSE, cache=TRUE, results='asis'}
fulldat$usemeta2 <- factor(fulldat$usemeta)
levels(fulldat$usemeta2) <- c("Other Coefficients", "Main Sample")
aux <- select(fulldat, usemeta2, indepvar2, elecsys2, method,
              year, published, instdesign) %>%
  rename(`Independent Variables` = indepvar2,
         `Year`                  = year,
         `Published work`        = published,
         `Estimation method`     = method,
         `Institutional Design`  = instdesign,
         `Electoral system`      = elecsys2)
aux$`Independent Variables` <- recode(aux$`Independent Variables`,
                                      `N` = "Lower Chamber Size",
                                      `K` = "Upper Chamber Size",
                                      `logN` = "Log of Lower Chamber Size")
aux$`Electoral system` <- recode(aux$`Electoral system`,
                                 `Non-Maj` = "Non-Majoritarian",
                                 `Maj` = "Majoritarian")
aux <- select(aux, usemeta2, `Independent Variables`, Year, `Published work`, `Estimation method`, `Institutional Design`, `Electoral system`)

aux3 <- descrTable(~.-usemeta2,
                   aux, y = aux$usemeta2,
                   show.p.overall = F,
                   show.all = T)
export2md2(aux3,
           caption = "Descriptive Statistics of Moderators",
           format  = "latex")
```

@@

# Meta-Analysis (Main Sample)

@@

# Meta-Analysis (Extended Sample)

@@

## Meta-Regressions (All Coefficients)

@@

## Comparing Coefficient Sizes and Dependent Variables

Finally, we run a simple linear regression to check whether there are
significant differences between effect sizes for our dependent variables.
Although the meta-regressions show that the difference is statistically
negligible, we can still witness larger or smaller coefficient sizes in
different models. The results below show that the differences are indeed mostly
negligible.

```{r, size="footnotesize", echo = FALSE, cache=TRUE}
aux <- dat
aux$depvar2 <- factor(aux$depvar2, levels = c('PCTGDP', 'ExpPC', 'logExpPC'))
summary(lm(coef~depvar2, data = aux))
```
